### 2024-07-24 doc/Thesis/chapter/04-computational-details.tex
feinschliff
finish editing 04 comp details

\section{Evolutionary Model-based Multiresponse Approach}
\label{sec:ss}
%\todo{for what?}
An evolutionary approach was chosen, namely a multi-objective 
\gls{pso} algorithm called \gls{emma}\cite{villanova2010function,Kennedy1995,Breiman1997,Carta2011}.
%
%"PSO is a population based heuristic inspired by the flocking behavior of birds. 
%To simulate the behavior of a swarm, each bird (or particle) is allowed to fly towards the optimum solution."\cite{villanova2010function}
%
Initially, the input parameters (independent variables), their boundaries and number of equidistant levels for each parameter are declared (see table \ref{tab:input}).
Next, the output variables (dependant variables), their weights in the objective function (the function which should be optimized) are specified and if they should be minimized or maximized is noted.
%
%An initial population of particles, i.e. experiments with certain parameters, is chosen out of the population space (space spanned by all possible combinations of input parameters), 
\begin{table}[htb]
	\centering
	\begin{tabular}{cc cc cc}
		\hline\hline
        $c_{zr}$ [\SI{22}{\milli\mol\per\liter}]	&$n_L$	&$T_{C}$[\oc{}]	&$v_{C}$[\mm{}/\s{}]	&$T_{cal}$[\oc{}]	&$v_{cal}$[\oc{}/\h{}]	\\
		\hline
		2				&4		&40					&10				&300				&120	\\
		3				&6		&50					&12				&400				&360	\\
		4				&8		&60					&14				&500				&600	\\
		5				&10		&70					&16				&					&840	\\
						&12		&80					&18				&					&1080	\\
						&		&					&20				&					&		\\
		\hline\hline
	\end{tabular}
	\caption{Discrete levels of each input parameter }
	\label{tab:input}
\end{table}

The \textit{optimizands} where chosen to be $\gamma$, $\rho$, $n_L$ and $v_{cal}$, 
(i.e. conducticity, pinhole density, coating layer count and heating rate)
where $\gamma$, $\rho$ and $n_L$ are to be minimized and $v_{cal}$ to be maximized.
%which all should be minimized except for $v_{cal}$.
The next step is to generate an initial population (ensemble of experiments), which is chosen randomly from the population space. 
The samples are produced, the \gls{iv} curves are measured and measurements evaluated according to section 
\ref{sec:exp} and the responses conducticity $\gamma$ (see eq. \ref{eq:gamma}), pinhole density $\rho_s$ (see eq. \ref{eq:rho}), 
$n_L$ (numbers of coating layers) and $v_{cal}$ (heating rate of calcination process in 
\oc{}/\minutes{}) are supplied to the program. 
The program, then, uses this data to estimate a response for each output variable 
for the entire population space
(and to choose a fraction of the initial population which is allowed to propagate).
%The response variables for the entire population space is calculated. 
The current population - each of the particles independently - 
are given a random velocity vector associated to them, which is directed to the best predicted sample. 
%moves towards the optimum solution.
The population for the next time step is generated and 
again the samples are produced, the \gls{iv} curves are measured and measurements evaluated.
%the experiments are again \td{executed, measured and evaluated. (unclear!)}
Each time step thus includes experiment identification, solution preparation, coating deposition and layer analysis.

>>>>

\section{Evolutionary Model-based Multiresponse Approach (EMMA)}
\label{sec:ss}
%\todo{for what?}
An evolutionary approach was chosen, namely a multi-objective 
\gls{pso} algorithm called \gls{emma}\cite{villanova2010function,Kennedy1995,Breiman1997,Carta2011}.
%
%"PSO is a population based heuristic inspired by the flocking behavior of birds. 
%To simulate the behavior of a swarm, each bird (or particle) is allowed to fly towards the optimum solution."\cite{villanova2010function}
%
Initially, the input parameters (independent variables), their boundaries and number of equidistant levels for each parameter are declared (see table \ref{tab:input}).
Next, the output variables (dependant variables), their weights in the objective function (the function which should be optimized) are specified and if they should be minimized or maximized is noted.
%
%An initial population of particles, i.e. experiments with certain parameters, is chosen out of the population space (space spanned by all possible combinations of input parameters), 
\begin{table}[htb]
	\centering
	\begin{tabular}{cc cc cc}
		\hline\hline
        $c_{zr}$ [\SI{22}{\milli\mol\per\liter}]	&$n_L$	&$T_{C}$[\oc{}]	&$v_{C}$[\mm{}/\s{}]	&$T_{cal}$[\oc{}]	&$v_{cal}$[\oc{}/\h{}]	\\
		\hline
		2				&4		&40					&10				&300				&120	\\
		3				&6		&50					&12				&400				&360	\\
		4				&8		&60					&14				&500				&600	\\
		5				&10		&70					&16				&					&840	\\
						&12		&80					&18				&					&1080	\\
						&		&					&20				&					&		\\
		\hline\hline
	\end{tabular}
	\caption{Discrete levels of each input parameter }
	\label{tab:input}
\end{table}

The \textit{optimizands} where chosen to be $\gamma$, $\rho$, $n_L$ and $v_{cal}$, 
(i.e. conducticity, pinhole density, number of coated layers and heating rate)
where $\gamma$, $\rho$ and $n_L$ are to be minimized and $v_{cal}$ to be maximized.
%which all should be minimized except for $v_{cal}$.
The next step is to generate an initial population (ensemble of experiments), which is chosen randomly from the population space. 
The samples are produced, the \gls{iv} curves are measured and the measurements evaluated according to section 
\ref{sec:exp}, yielding the quantities 
$\gamma$, $\rho_s$, $n_L$ and $v_{cal}$, which were used as inputs for the program.
% and the responses conducticity $\gamma$ (see eq. \ref{eq:gamma}), pinhole density $\rho_s$ (see eq. \ref{eq:rho}), $n_L$ (numbers of coating layers) and $v_{cal}$ (heating rate of calcination process in \oc{}/\minutes{}) are supplied to the program.

The program, then, uses this data to estimate a response for each output variable 
for the entire population space
(and to choose a fraction of the initial population which is allowed to propagate).
%The response variables for the entire population space is calculated. 
The current population - each of the particles independently - 
are given a random velocity vector associated to them, which is directed to the best predicted sample. 
%moves towards the optimum solution.
The population for the next time step is generated and 
again the samples are produced, the \gls{iv} curves are measured and measurements evaluated.
%the experiments are again \td{executed, measured and evaluated. (unclear!)}
Each time step thus includes experiment identification, solution preparation, coating deposition and layer analysis.
